### 2021-05-02 Paper/Results.tex
latex update

Moving on to the MSCI based portfolio, a two-pass sort was also used to assess the sensitivity and risk premia on the ESG portfolio on both size and  beta porflio

\begin{center}
    \paperspacingnarrow
\input{Code/data/All_Industry_FF_pass_2}\\
\textbf{Table 7:} SIC top 10\% minus bottom 10\%
    \paperspacingwide
\end{center}

>>>>

Moving on to the second stage of the analysis, I constructed an ESG factor out of the MSCI ESG ratings to capture a more holistic view of ESG risk. I created this factor by taking the top 10\% of MSCI EGS rated companies and subtracted them from the bottom 10\% of firms rated by the MSCI. I repeated the methodology above for the regression analysis. I  regressed two sets of two-pass regression analyses one on beta-sized portfolios and another on size-based portfolios. In the first pass results from the new factor, the beta portfolio demonstrated a decrease in sensitivity as the betas grew; however, the size-based portfolios did not experience any real pattern governing the decile and the sensitivity. In the case of the size-based portfolios, some of the sensitivity figures were positive while others were negative. Table 4 represents a second stage two-pass sort regression output from this table it is clear that

\begin{center}
    \paperspacingnarrow
\input{Code/data/All_Industry_FF_pass_2}\\
\textbf{Table 4:} SIC top 10\% minus bottom 10\%
    \paperspacingwide
\end{center}

### 2021-05-02 Paper/robustness.tex
big push in latex
latex update

>>>>

 dicuss limitation of only one set of ESG factors for MSCI

 we used the Size deciles on a go froward basis when analysis the data as the statistical relationship was more apparent

 \textbf{Analysis for the w/o ESG on the data}\\
 \textbf{yearly effect}\\

 \textbf{MSCI data 2019 beyond}\\

 \textbf{MSCI SIC level analysis}\\

 problems we can never solve for both of these indexes does not do a great job capturing small companies so size might be a bit of a probelm overall as the small companies do not have ther ESG scores baked in as MSCI does not have the resources to rank every company
